---
title: "Testing out metajam fuction"
output: html_document
date: "2022-08-24"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

The metajam R package relies on the dataONE API to download data and metadata into your R Environment. It is currently supporting KNB, ADC and EDI repositories because they rely on the metadata standard EML.

```{r}

library(metajam)
library(here)

data_url <- "https://knb.ecoinformatics.org/knb/d1/mn/v2/object/urn%3Auuid%3A7fc6f6db-c5ea-426a-a743-1f2edafb43b8"
data_path <- "~/courses/eds214/api-practice"


alaska_language <- download_d1_data(data_url = data_url, path = data_path)

```
Reading in the data now

```{r}

my_data <- read_d1_files("~/courses/eds214/api-practice/household_language_data/")

```


```{r}

# creating a data frame from the data

dataframe <- my_data$data

# Write a piece of code that will compute the percentage of Alaskan household speaking only English for the year 2009 to 2015

class(dataframe$Year)

plot_info <- dataframe %>% 
  group_by(Year) %>% 
  summarize(total_new = sum(total),
            english_speakers = sum(speak_only_english),
            percentage = ((english_speakers / total_new) * 100)))


plot_info_filter <- plot_info %>% 
  filter(Year == c(2009:2015))
  
  
  
